Report

### 2023-05-13 implementation/Report.Rmd
finalized the report for 8 scenarios

```{r setup, include=FALSE, cache=TRUE}
## Global options
library(reticulate)
library(knitr)
library(flexdashboard)
library(scales)
library(here)
library(tidyverse)
library(readr)
library(plotly)
library(tidyverse)
knitr::opts_chunk$set(cache = TRUE)
source(here('modules','data_funcs.R'))

@@

# # NO CUU - OR * 1.1
# modif <- '0-1.1'
# dt_pl_n11 <- generate_summary(path, modif, dur, warm, repl)
# dt_sa_n11 <- generate_summary_sa(path, modif, dur, warm, repl)
# dt_zs_n11 <- generate_summary_zs(path, modif, FALSE)
# 
# # NO CUU - OR * 1.2
# modif <- '0-1.2'
# dt_pl_n12 <- generate_summary(path, modif, dur, warm, repl)
# dt_sa_n12 <- generate_summary_sa(path, modif, dur, warm, repl)
# dt_zs_n12 <- generate_summary_zs(path, modif, FALSE)
# 
# # NO CUU - OR * 1.3
# modif <- '0-1.3'
# dt_pl_n13 <- generate_summary(path, modif, dur, warm, repl)
# dt_sa_n13 <- generate_summary_sa(path, modif, dur, warm, repl)
# dt_zs_n13 <- generate_summary_zs(path, modif, FALSE)
# 
# 
# 
# # CUU - OR * 1
# modif <- '1000-1'
# dt_pl_y10 <- generate_summary(path, modif, dur, warm, repl)
# dt_sa_y10 <- generate_summary_sa(path, modif, dur, warm, repl)
# dt_zs_y10 <- generate_summary_zs(path, modif, TRUE)
# 
# # CUU - OR * 1.1
# modif <- '1000-1.1'
# dt_pl_y11 <- generate_summary(path, modif, dur, warm, repl)
# dt_sa_y11 <- generate_summary_sa(path, modif, dur, warm, repl)
# dt_zs_y11 <- generate_summary_zs(path, modif, TRUE)
# 
# # CUU - OR * 1.2
# modif <- '1000-1.2'
# dt_pl_y12 <- generate_summary(path, modif, dur, warm, repl)
# dt_sa_y12 <- generate_summary_sa(path, modif, dur, warm, repl)
# dt_zs_y12 <- generate_summary_zs(path, modif, TRUE)
# 
# # CUU - OR * 1.3
# modif <- '1000-1.3'
# dt_pl_y13 <- generate_summary(path, modif, dur, warm, repl)
# dt_sa_y13 <- generate_summary_sa(path, modif, dur, warm, repl)
# dt_zs_y13 <- generate_summary_zs(path, modif, TRUE)

@@

nPen, OR*1
=======================================================================

@@

### Policy Graph

### Policy Description

nPen, OR*1.1
=======================================================================

@@

### Policy Graph

### Policy Description

nPen, OR*1.2
=======================================================================

@@

### Policy Graph

### Policy Description

nPen, OR*1.3
=======================================================================

@@

### Policy Graph

### Policy Description

Pen, OR*1
=======================================================================

@@

### Policy Graph

### Policy Description

Pen, OR*1.1
=======================================================================

@@

### Policy Graph

### Policy Description

Pen, OR*1.2
=======================================================================

@@

### Policy Graph

### Policy Description

Pen, OR*1.3
=======================================================================

@@

### Policy Graph

### Policy Description

<!-- # R1R2 Report -->
<!-- This model is the default model that does not penalize bed under utilization -->

<!-- ## Policy Description -->
<!-- The description will be based on the following graphs (both of them are for M of 0 only): -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- R1R2_policy -->
<!-- ``` -->

<!-- The top graphs show MDP policy, and the graphs below show Myopic policy. -->

<!-- The graph on the left shows in which days the policy will allow scheduling. If the value is below 0 - the model will allow scheduling, otherwise the model will keep patients in the waitlist. Thus this policy **will only schedule into week 1 and week 2**. The plot on the right shows the approximate priority of different surgeries. The lower the surgery is on the list the more likely it is to be scheduled first. The following is the order: -->

<!-- - Surgery 6, Complexity 2 -->
<!-- - Surgery 6, Complexity 1 -->
<!-- - Surgery 1, Complexity 1 -->
<!-- - Surgery 1, Complexity 2 -->
<!-- - Surgery 4, Complexity 1 -->
<!-- - Surgery 4, Complexity 2 -->

<!-- For Myopic, it is changed such that the entire horizon is filled. And the graph on the right shows the approximate order of scheduling priority. It appears to be very similar to MDP. -->

<!-- Additionally the following graphs give some insights on how the policy makes decision -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- R1R2_sa$res_plot$sched_plt -->
<!-- ``` -->

<!-- ## Policy Results -->
<!-- ### Wait Times in weeks -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- kable(R1R2$results$pw) -->
<!-- ``` -->

<!-- ### Wait List Size -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- kable(R1R2$results$wtl) -->
<!-- ``` -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- R1R2_sa$res_plot$waitlist_plt -->
<!-- ``` -->

<!-- ### Utilization -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- kable(R1R2$results$util) -->
<!-- ``` -->

<!-- ### Reschedules as percentage of arrivals & Total Reschedules -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- kable(R1R2$results$rsc) -->
<!-- ``` -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- R1R2_sa$res_plot$rsc_plt %>% ggplotly() -->
<!-- ``` -->

<!-- ### Transitions per week -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- kable(R1R2$results$tr) -->
<!-- ``` -->

<!-- # R1R2R3 Report -->
<!-- In addition to the parameters above, this model penalizes bed under utilization in the first period -->

<!-- ## Policy Description -->
<!-- <!-- The description will be based on the following graphs: --> -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- R1R2R3_policy -->
<!-- ``` -->

<!-- Additionally the following graphs give some insights on how the policy makes decision -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- R1R2R3_sa$res_plot$sched_plt -->
<!-- ``` -->

<!-- ## Policy Results -->

<!-- ### Wait Times in weeks -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- kable(R1R2R3$results$pw) -->
<!-- ``` -->

<!-- ### Wait List Size -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- kable(R1R2R3$results$wtl) -->
<!-- ``` -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- R1R2R3_sa$res_plot$waitlist_plt -->
<!-- ``` -->

<!-- ### Utilization -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- kable(R1R2R3$results$util) -->
<!-- ``` -->

<!-- ### Reschedules as percentage of arrivals & Total Reschedules -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- kable(R1R2R3$results$rsc) -->
<!-- ``` -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- R1R2R3_sa$res_plot$rsc_plt %>% ggplotly() -->
<!-- ``` -->

<!-- ### Transitions per week -->
<!-- ```{r echo=FALSE, cache=FALSE} -->
<!-- kable(R1R2R3$results$tr) -->
<!-- ``` -->

>>>>

```{r setup, include=FALSE}
## Global options
library(reticulate)
library(knitr)
library(flexdashboard)
library(scales)
library(here)
library(tidyverse)
library(readr)
library(plotly)
library(tidyverse)
knitr::opts_chunk$set(cache = TRUE)
source(here('modules','data_funcs.R'))

@@

# NO CUU - OR * 1.1
modif <- '0-1.1'
dt_pl_n11 <- generate_summary(path, modif, dur, warm, repl)
dt_sa_n11 <- generate_summary_sa(path, modif, dur, warm, repl)
dt_zs_n11 <- generate_summary_zs(path, modif, FALSE)

# NO CUU - OR * 1.2
modif <- '0-1.2'
dt_pl_n12 <- generate_summary(path, modif, dur, warm, repl)
dt_sa_n12 <- generate_summary_sa(path, modif, dur, warm, repl)
dt_zs_n12 <- generate_summary_zs(path, modif, FALSE)

# NO CUU - OR * 1.3
modif <- '0-1.3'
dt_pl_n13 <- generate_summary(path, modif, dur, warm, repl)
dt_sa_n13 <- generate_summary_sa(path, modif, dur, warm, repl)
dt_zs_n13 <- generate_summary_zs(path, modif, FALSE)

# CUU - OR * 1
modif <- '1000-1'
dt_pl_y10 <- generate_summary(path, modif, dur, warm, repl)
dt_sa_y10 <- generate_summary_sa(path, modif, dur, warm, repl)
dt_zs_y10 <- generate_summary_zs(path, modif, TRUE)

# CUU - OR * 1.1
modif <- '1000-1.1'
dt_pl_y11 <- generate_summary(path, modif, dur, warm, repl)
dt_sa_y11 <- generate_summary_sa(path, modif, dur, warm, repl)
dt_zs_y11 <- generate_summary_zs(path, modif, TRUE)

# CUU - OR * 1.2
modif <- '1000-1.2'
dt_pl_y12 <- generate_summary(path, modif, dur, warm, repl)
dt_sa_y12 <- generate_summary_sa(path, modif, dur, warm, repl)
dt_zs_y12 <- generate_summary_zs(path, modif, TRUE)

# CUU - OR * 1.3
modif <- '1000-1.3'
dt_pl_y13 <- generate_summary(path, modif, dur, warm, repl)
dt_sa_y13 <- generate_summary_sa(path, modif, dur, warm, repl)
dt_zs_y13 <- generate_summary_zs(path, modif, TRUE)

@@

NP, 1
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Policy Description
The policy description is based on a graph to the right

* The left column shows MDP policy, the right column shows Myopic Policy
* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
* The bottom row shows in which days the policy will allow scheduling.
* The top row shows approximate order of patient scheduling.

Additionally the far right graph shows the approximate decision making

### Policy Math Graph

### Policy Evidence Graph

```{r echo=FALSE}
dt_sa_n10$res_plot$sched_plt %>% ggplotly()
```

@@

### Wait Times in weeks
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n10$results$pw)
```

### Wait List Size
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n10$results$wtl)
```

### Transitions per week
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n10$results$tr)
```

### Utilization
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n10$results$util)
```

@@

### Reschedules
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n10$results$rsc)
```

### Wait List Size by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_n10$res_plot$waitlist_plt %>% ggplotly()
```

### Reschedules by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_n10$res_plot$rsc_plt %>% ggplotly()
```

NP, 1.1
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Policy Description
The policy description is based on a graph to the right

* The left column shows MDP policy, the right column shows Myopic Policy
* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
* The bottom row shows in which days the policy will allow scheduling.
* The top row shows approximate order of patient scheduling.

Additionally the far right graph shows the approximate decision making

### Policy Math Graph

```{r echo=FALSE}
dt_zs_n11$zf_plt %>% ggplotly()
```

### Policy Evidence Graph

```{r echo=FALSE}
dt_sa_n11$res_plot$sched_plt %>% ggplotly()
```

@@

### Wait Times in weeks
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n11$results$pw)
```

### Wait List Size
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n11$results$wtl)
```

### Transitions per week
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n11$results$tr)
```

### Utilization
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n11$results$util)
```

@@

### Reschedules
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n11$results$rsc)
```

### Wait List Size by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_n11$res_plot$waitlist_plt %>% ggplotly()
```

### Reschedules by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_n11$res_plot$rsc_plt %>% ggplotly()
```

NP, 1.2
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Policy Description
The policy description is based on a graph to the right

* The left column shows MDP policy, the right column shows Myopic Policy
* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
* The bottom row shows in which days the policy will allow scheduling.
* The top row shows approximate order of patient scheduling.

Additionally the far right graph shows the approximate decision making

### Policy Math Graph

```{r echo=FALSE}
dt_zs_n12$zf_plt %>% ggplotly()
```

### Policy Evidence Graph

```{r echo=FALSE}
dt_sa_n12$res_plot$sched_plt %>% ggplotly()
```

@@

### Wait Times in weeks
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n12$results$pw)
```

### Wait List Size
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n12$results$wtl)
```

### Transitions per week
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n12$results$tr)
```

### Utilization
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n12$results$util)
```

@@

### Reschedules
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n12$results$rsc)
```

### Wait List Size by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_n12$res_plot$waitlist_plt %>% ggplotly()
```

### Reschedules by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_n12$res_plot$rsc_plt %>% ggplotly()
```

NP, 1.3
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Policy Description
The policy description is based on a graph to the right

* The left column shows MDP policy, the right column shows Myopic Policy
* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
* The bottom row shows in which days the policy will allow scheduling.
* The top row shows approximate order of patient scheduling.

Additionally the far right graph shows the approximate decision making

### Policy Math Graph

```{r echo=FALSE}
dt_zs_n13$zf_plt %>% ggplotly()
```

### Policy Evidence Graph

```{r echo=FALSE}
dt_sa_n13$res_plot$sched_plt %>% ggplotly()
```

@@

### Wait Times in weeks
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n13$results$pw)
```

### Wait List Size
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n13$results$wtl)
```

### Transitions per week
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n13$results$tr)
```

### Utilization
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n13$results$util)
```

@@

### Reschedules
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_n13$results$rsc)
```

### Wait List Size by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_n13$res_plot$waitlist_plt %>% ggplotly()
```

### Reschedules by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_n13$res_plot$rsc_plt %>% ggplotly()
```

P, 1
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Policy Description
The policy description is based on a graph to the right

* The left column shows MDP policy, the right column shows Myopic Policy
* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
* The bottom row shows in which days the policy will allow scheduling.
* The top row shows approximate order of patient scheduling.

Additionally the far right graph shows the approximate decision making

### Policy Math Graph

```{r echo=FALSE}
dt_zs_y10$zf_plt %>% ggplotly()
```

### Policy Evidence Graph

```{r echo=FALSE}
dt_sa_y10$res_plot$sched_plt %>% ggplotly()
```

### Wait Times in weeks
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y10$results$pw)
```

### Wait List Size
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y10$results$wtl)
```

### Transitions per week
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y10$results$tr)
```

### Utilization
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y10$results$util)
```

### Reschedules
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y10$results$rsc)
```

### Wait List Size by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_y10$res_plot$waitlist_plt %>% ggplotly()
```

### Reschedules by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_y10$res_plot$rsc_plt %>% ggplotly()
```

P, 1.1
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Policy Description
The policy description is based on a graph to the right

* The left column shows MDP policy, the right column shows Myopic Policy
* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
* The bottom row shows in which days the policy will allow scheduling.
* The top row shows approximate order of patient scheduling.

Additionally the far right graph shows the approximate decision making

### Policy Math Graph

```{r echo=FALSE}
dt_zs_y11$zf_plt %>% ggplotly()
```

### Policy Evidence Graph

```{r echo=FALSE}
dt_sa_y11$res_plot$sched_plt %>% ggplotly()
```

### Wait Times in weeks
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y11$results$pw)
```

### Wait List Size
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y11$results$wtl)
```

### Transitions per week
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y11$results$tr)
```

### Utilization
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y11$results$util)
```

### Reschedules
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y11$results$rsc)
```

### Wait List Size by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_y11$res_plot$waitlist_plt %>% ggplotly()
```

### Reschedules by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_y11$res_plot$rsc_plt %>% ggplotly()
```

P, 1.2
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Policy Description
The policy description is based on a graph to the right

* The left column shows MDP policy, the right column shows Myopic Policy
* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
* The bottom row shows in which days the policy will allow scheduling.
* The top row shows approximate order of patient scheduling.

Additionally the far right graph shows the approximate decision making

### Policy Math Graph

```{r echo=FALSE}
dt_zs_y12$zf_plt %>% ggplotly()
```

### Policy Evidence Graph

```{r echo=FALSE}
dt_sa_y12$res_plot$sched_plt %>% ggplotly()
```

### Wait Times in weeks
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y12$results$pw)
```

### Wait List Size
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y12$results$wtl)
```

### Transitions per week
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y12$results$tr)
```

### Utilization
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y12$results$util)
```

### Reschedules
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y12$results$rsc)
```

### Wait List Size by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_y12$res_plot$waitlist_plt %>% ggplotly()
```

### Reschedules by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_y12$res_plot$rsc_plt %>% ggplotly()
```

P, 1.3
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Policy Description
The policy description is based on a graph to the right

* The left column shows MDP policy, the right column shows Myopic Policy
* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
* The bottom row shows in which days the policy will allow scheduling.
* The top row shows approximate order of patient scheduling.

Additionally the far right graph shows the approximate decision making

### Policy Math Graph

```{r echo=FALSE}
dt_zs_y13$zf_plt %>% ggplotly()
```

### Policy Evidence Graph

```{r echo=FALSE}
dt_sa_y13$res_plot$sched_plt %>% ggplotly()
```

### Wait Times in weeks
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y13$results$pw)
```

### Wait List Size
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y13$results$wtl)
```

### Transitions per week
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y13$results$tr)
```

### Utilization
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y13$results$util)
```

### Reschedules
```{r echo=FALSE, cache=FALSE}
kable(dt_pl_y13$results$rsc)
```

### Wait List Size by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_y13$res_plot$waitlist_plt %>% ggplotly()
```

### Reschedules by Group
```{r echo=FALSE, cache=FALSE}
dt_sa_y13$res_plot$rsc_plt %>% ggplotly()
```
